---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# susographql

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/michael-cw/susographql/workflows/R-CMD-check/badge.svg)](https://github.com/michael-cw/susographql/actions)
<!-- badges: end -->

The susographql allows you to use the Survey Solutions GraphQL endpoints. A detailed documentation can be found [here](https://demo.mysurvey.solutions/graphql/), the package itself only contains a very rudimentary documentation. 

This is currently a beta version, which means the package is under (active) development. It is recommended that only users who are familiar on how to use packages in development should use this package. And certainly users are also invited to suggest improvements or to add their own functions to the package by forking.

## Installation

* Install R: https://cran.r-project.org/mirrors.html (version 4.1.1 or greater)

* Install R Studio: https://rstudio.com/products/rstudio/download/ (version 1.2.5001-3 or newer)

* Make sure the *devtools* package is installed, if not install it with:

```{r devtoolsinst,eval=FALSE, echo=TRUE}
install.packages("devtools")

```


* After that install the actual package:

```{r install,eval=FALSE, echo=TRUE}
devtools::install_github("michael-cw/susographql")

```

