---
title: "Using skip and take in a loop"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using skip and take in a loop}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)

ep<-Sys.getenv("SUSO_API_EP")
usr<-Sys.getenv("SUSO_API_USER")
pass<-Sys.getenv("SUSO_API_PASSWORD")
```


```{css, echo=FALSE}

p {
  text-align: justify !important;
}

```


## Quick credentials check

```{r pwcheck}
library(susographql)

suso_gql_pwcheck(
  endpoint = ep,
  user = usr,
  password = pass,
  workspace = "primary"
)

```


## Assignment list 1 (simple)

Exporting a list of assignments usually contains more than 100 rows, and a single API call would not allow us to get a complete list, as the limit (parameter take) is 100. To still get all the assignments, we need to make use of the skip parameter. In the example bellow we will apply the following strategy:

1. We do a single API call, and get the first 100 assignments, plus the parameters totalCount/filteredCount.
2. We then get the total number and calculate the remaining number of assignments on the server
3. We create a loop, and increase the number to skip always by 100

One problem in the example bellow is the column calendarEvent which is a nested data.frame column. For the simple solution, we just delete it. 

```{r loopsimple}

asslist<-suso_gql_assignments(
  endpoint = ep,
  user = usr, password = pass, workspace = "primary",
  take = 100
)

# tot count (safer to always use filtered count)
tot<-asslist$assignments$filteredCount
# max lengt is 100
rest<-tot - nrow(asslist$assignments$nodes)
# number of loops
n_loops<-ceiling(rest/100)
# skip/take augment
ass_loop<-function(i) {
  asslist<-suso_gql_assignments(
    endpoint = ep,
    user = usr, password = pass, workspace = "primary",
    skip = 100*i, take = 100
  )
  # remove calenderevent otherwise rbind gets difficult
  dout<-asslist$assignments$nodes
  dout$calendarEvent<-NULL
  return(dout)

}
# lapply for the loop
asslist_rest<-lapply(1:n_loops, ass_loop)
# bind the last two lists
asslist_rest <- do.call(rbind, c(asslist_rest, make.row.names = FALSE))

# bind the first df and the result of the rest into 1 (remove cal event first)
asslist<-asslist$assignments$nodes
asslist$calendarEvent<-NULL
asslist<-rbind(asslist, asslist_rest)

# Compare the final number of rows with the total
tot==nrow(asslist)

# Column names
names(asslist)

```

As you can see, the total count (when using a filter, use filteredCount) extracted at the beginning is the same as the number of rows of the final data.frame.

## Assignment list 2 (not so simple)

Same as above, however now we keep the nested data.frame column.

```{r loopcomplex}

# 1. get first list (limit is automatic 100 but we use the parameter here for demonstration)
asslist<-suso_gql_assignments(
  endpoint = "https://michael-wild-demo.mysurvey.solutions/graphql",
  user = "apiUser", password = "Nitro12345", workspace = "primary",
  take = 100
)

# tot count (safer to always use filtered count)
tot<-asslist$assignments$filteredCount
# max lengt is 100
rest<-tot - nrow(asslist$assignments$nodes)
# number of loops
n_loops<-ceiling(rest/100)
# skip/take augment
ass_loop<-function(i) {
  asslist<-suso_gql_assignments(
    endpoint = "https://michael-wild-demo.mysurvey.solutions/graphql",
    user = "apiUser", password = "Nitro12345", workspace = "primary",
    skip = 100*i, take = 100
  )
  # remove calenderevent otherwise rbind gets difficult
  dout<-asslist$assignments$nodes
  #dout$calendarEvent<-NULL
  return(dout)

}

# lapply for the loop
asslist_rest<-lapply(1:n_loops, ass_loop)

# Function for rbind with nested data.frames
row_bind_list <- function(df_list) {
  # Check if all data frames in the list have the same structure
  if (!all(sapply(df_list, function(x) all(names(x) == names(df_list[[1]]))))) {
    stop("All data frames in the list must have the same columns.")
  }

  # Bind regular columns and nested data.frame columns separately
  regular_cols <- which(!sapply(df_list[[1]], is.data.frame))
  nested_cols <- which(sapply(df_list[[1]], is.data.frame))

  # Bind regular columns
  regular_df <- do.call(rbind, lapply(df_list, function(df) df[, regular_cols, drop = FALSE]))

  # Bind nested data.frame columns
  nested_dfs <- lapply(nested_cols, function(ncol) {
    do.call(rbind, lapply(df_list, function(df) df[[ncol]]))
  })

  # Combine regular and nested columns into one data frame
  bound_df <- cbind(regular_df, setNames(nested_dfs, names(df_list[[1]])[nested_cols]))

  return(bound_df)
}

# Add the first 100 & bind the data.frames
asslist_rest[[(n_loops+1)]]<-asslist$assignments$nodes
asslist<-row_bind_list(asslist_rest)

# Compare the final number of rows with the total
tot==nrow(asslist)

# Column names
names(asslist)


```

Again same result as above, however the calendarEvent nested data.frame columns are now included. Though if you are not using calendar events in your survey, then this column would not be relevant for you, and the first solutions is sufficient.


